\chapter{Assignment 1: Gattaca}

I've watched the movie Gattaca (together with my fiancée) and surprisingly We've really enjoyed it. 
I first found "sad" how the father of newborn Vincent, after he heard (after a blood analysis) that Vincent has an heart disease and will live no longer the 30/35 years (so it chose to name it Vincent instead of Anton which is the Father's name).
After this, they chose to have another child that can have the name Anton and it was chosen via genetic selection.

During the childhood, Vincent was always seen as inferior to his brother Anton, because he was not genetically perfect as him, his brother always was "mocking" Vincent because is better and stronger in anything, intelligent and he can't do nothing against this.
Also the scene for where the parents measure their height, Vincent saw that is marked that he is shorter than Anton and he deleted its mark (Anton being taller, meant that is better than Vincent, stronger).
But there were moments when Vincent was somehow reversing the medal, like in the swimming scenes where almost always Vincent was winning because he had nothing to lose; is like Anton's perfection made him cautious, while Vincent's "flaw" made him fearless; he won because he was the older brother who refused to accept a diminished version of himself.

Vincent meets up with Jerome which was a genetically perfect person, but he had an accident and he can't walk anymore. So Vincent takes his place and he goes to Gattaca. 

At the end of the film, Vincent gets caught (also by his brother Anton of this, but again, they do the swimming scene and again, wins).
Gattaca accepts Vincent as he is (masking as Valid via Jerome's profile), and he manages to leave for Titan.

The thing is that, in that film, the DNA is seen more like a Biography thing instead of Biology, where based on it you can literally see what the child can do in his life, what will be capable of and what possible diseases can have or has. For example, when the medic read that 99% Vincent will have an heart disease, the parent started somehow to not being him as a child but as a defection.

Another thing Is related to the fact that the DNA is a witness that betrays you constantly; Vincent has to shave, scrub with the brush, and burn his dead cells every morning. The fact that the security found an eyelash near the body of the killed coordinator and triggered a manhunt against Vincent without knowing it... privacy no longer exists.

I do not want to forget about Irene also, because, her still being a valid one, is invalid because she has a minor hearth disease that denies her to fly in the space. This kinda lets me see tha, although you can control everything, you can't control biology even if you want.

At the end of the film, the swimming race against Vincent and Anton let me think that DNA can't control the will, the desire of a man. Anton loses because he is cautious because he knows that he can't die; Vincent swims "without saving energy for the return". Is like that the human spirit is the only variable that biology can't control.