\documentclass{beamer}
\usetheme{Madrid}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\title{Treating Depression Without Hallucinations}
\subtitle{A New Biotechnology Approach}
\author{Murariu Andrei Stefanel}
\date{March 25, 2026}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Introduction to the News}
\begin{itemize}
    \item \textbf{Source:} American Chemical Society via ScienceDaily.
    \item \textbf{Date:} March 8, 2026.
    \item \textbf{Topic:} A new drug based on "magic mushrooms" that treats depression but stops hallucinations.
    \item \textbf{Area:} Biotechnology and Pharmacology.
\end{itemize}
\vspace{0.3cm}
\end{frame}

\begin{frame}{The Problem with Current Treatments}
\begin{itemize}
    \item Magic mushrooms contain a chemical called psilocybin.
    \item The body turns this into psilocin, which goes to the brain.
    \item It helps with severe depression and anxiety.
    \item \textbf{The Problem:} It causes intense hallucinations (seeing things that are not real).
    \item Patients are afraid, and it requires constant medical supervision.
\end{itemize}
\end{frame}

\begin{frame}{The Biotechnology Solution}
\begin{itemize}
    \item Scientists modified the chemical structure of psilocin.
    \item They tested many variations in the lab.
    \item They discovered a new molecule called \textbf{Compound 4e}.
    \item Compound 4e releases the medicine very slowly into the body.
    \item It still connects to serotonin receptors (the "happiness" areas of the brain).
\end{itemize}
\end{frame}

\begin{frame}{Testing on Mice}
\begin{itemize}
    \item Scientists compared regular psilocybin with Compound 4e in mice.
    \item They checked for hallucinations by counting "head twitches" in the mice.
    \item Mice taking Compound 4e had very few head twitches.
    \item The medicine still reached their brains successfully over 48 hours.
\end{itemize}
\vspace{0.3cm}
\end{frame}

\begin{frame}{Conclusion and Impact}
\begin{itemize}
    \item We can now use the medical power of mushrooms safely.
    \item Patients won't experience scary "trips".
    \item Treatment can happen at home, making it cheaper and easier to access.
    \item This is a great example of modifying biology to remove unwanted side effects.
\end{itemize}
\end{frame}

\begin{frame}{References}
\textbf{Reference:} \\
\vspace{0.5cm}
American Chemical Society. (2026, March 8). A new ``magic mushroom'' drug could treat depression without psychedelic hallucinations. \textit{ScienceDaily}. Retrieved March 22, 2026, from https://www.sciencedaily.com/releases/2026/03/260307213232.htm
\end{frame}

\end{document}